Supplementary Material for Asymmetry paper

### 2020-05-11 Supplementary/Sup_mat.Rmd
Added new plot to supmat

df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p,
             colour = diff)) + 
  geom_line() + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")
```

>>>>

plt_both <- df_distributions %>% 
  mutate(diff = as.factor(diff)) %>%
  ggplot(aes(x_vals, p)) + 
  geom_histogram(data = df_part2, 
                 aes(x = (norm_pos + 1)/2,
                     y = ..density..),
                 binwidth = .1,
                 colour = "blue",
                 fill = "blue",
                 alpha = .2) + 
  geom_line(aes(colour = diff)) + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) +
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom")

plt_dists <- df_distributions %>% 
  mutate(diff = as.factor(diff)) %>% 
  ggplot(aes(x_vals, p)) + 
  geom_line(aes(colour = diff)) + 
  theme_bw() + 
  see::scale_color_flat() +
  guides(colour = guide_legend("Difference")) + 
  theme(
    axis.title = element_blank(),
    legend.position = "bottom"
  )

plt_hist <- df_distributions %>% 
  filter(diff == 0) %>% 
  mutate(diff = as.factor(diff)) %>% 
  ggplot(aes(x_vals, p)) + 
  geom_line(aes(colour = diff)) + 
  see::scale_color_flat() + 
  theme_bw() + 
  geom_histogram(data = df_part2, 
                 aes(x = (norm_pos + 1)/2, y = ..density..),
                 binwidth = .1,
                 colour = "blue", 
                 fill = "blue",
                 alpha = .2) + 
  theme(
    legend.position = "none",
    axis.title = element_blank()
    )

# plt_hist <- df_part2 %>% 
#   ggplot(aes((norm_pos +1)/2, y = ..density..)) + 
#   geom_histogram(binwidth = .1, 
#                  colour = "blue",
#                  fill = "blue",
#                  alpha = .2) + 
#   theme_bw() + 
#   theme(
#     axis.title = element_blank()
#   )

gridExtra::grid.arrange(plt_hist, plt_dists, ncol = 2)
```
